---
title       : Course Enrollment History
subtitle    : Interactive Chart and Data Table in a Web Application
author      : Edgar
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Why?

- Problem: Subject Coordinator requested historical course enrollment data to facilitate planning. It took weeks to deliver the report.
- Goal: Provide subject coordinators and faculty administrators with timely access to the same data, and other tools for Enrollment Management.
- Technology: What is most cost effective way of providing data access to many people?

--- .class #id 

## How?

1. Enrollment data extracted from school ERP system to a text file
2. Used R to automate processing of the data
3. Used R's Shiny package to create interactive web app
4. Published prototype web app on Github. 
5. Ideal is a secure intranet server within the school network.

--- .class #id

## Chart Sample
How effective is the planning and utilization of capacity?
```{r echo=FALSE}
library(ggplot2)
library(reshape2)
d <- read.csv("enrolldata.csv")
select <- d[d$Subject=="ABCD"&d$AcyrCode>=1995&d$AcyrCode<2015,]
pdata <- aggregate(select[,c(6,7)], list(select$Term), sum)
pdata <- melt(pdata, id="Group.1")
p <- ggplot(pdata, aes(Group.1, value, color=variable))+geom_line()
p <- p + labs(x="Term", y="Enrollment", title="ABCD Enrollment per Term, Academic Years 1995-2015")
p
```

--- .class #id

## Detailed Data Table
Investigate trends in the data, or find "dirty data"
```{r, echo=FALSE, results="asis"}
library(xtable)
print(xtable(select[1:10,1:7]), type="html")
```
